Realistically Interesting Domains for Probabilistic Planners

### 2014-04-10 FinalPaper/paper.tex
Rewritten future work

>>>>

To empirically test which planner performs best for a certain domain,
experiments needs to be executed. The domain description language would be RDDL
\cite{Sanner:RDDL}, as \textsc{Gourmand} already works natively with it.
FF-Replan does not work with RDDL, but PPDDL instead. FF-Replan could be
re-implemented in the \textsc{Gourmand} framework, using the FF heuristic found
in mGPT \cite{bonet2011planning}. Another possibility is to implement the
domain in both languages and carefully assess if both implementations are fair.
The two metrics that need to be measured are the rate the goal is reached (and does
not reach dead ends) and the online execution time.
